A multi-dimensional extension of the Lightweight Temporal Compression method

### 2018-10-11 paper.tex
write in method

\section{Implementation}
Our code is available at ... (make a clean release!)

\subsection{Multidimensional LTC with Manhattan distance}
In practice, Multidimensional LTC is same as implementing LTC in each 
parameter respectively. But we did some changes in our method. Assume 
$(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with 
n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., 
z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming 
data to $t_1$ time-stamp and create a bounding box for recording 
overlapping range which includes upper and lower bound for each 
dimension base on $t_1$. cause the time different between two adjacent 
data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + 
\frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$. 
After that updating tolerance range by adding designed error margin 
which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, 
j={1...n}$ with Manhattan distance. checking if there is overlap 
between tolerance and bounding box.The algorithm is as follows.

\note{not clear about Manhattan distance, in my opinion for each axis the distance less than $EPSILEN/t_i-t_0$ + bounding box length}

@@

\subsection{Multidimensional LTC with Euclidean distance} 
In Euclidean distance version, we also map the coming data into same time-stamp. The difference with Manhattan distance version is that recording overlapping part with a post-designed model is difficult, which need retain several arcs in 2-dimension, or convex surfaces in 3-dimension. In our method, we will record all tolerance range for every mapped data which come from base data point until coming data point, in order to checking if there is intersection among them. In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
\begin{itemize}
\item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk. After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data. Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
\item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis. So In 3-dimension whether \textit{n} balls intersect need to be check.
\end{itemize}

At first, let us solve the \textit{n} disks intersect. We use a algorithm which is based on plane sweep and dichotomy. Assume a disk include center$(x,y)$ and radius $r$. The pseudo-code in Algorithm 1.
\begin{algorithm}
    \caption{whether disks intersect}
    \begin{flushleft}
        \textbf{Input:} $l$ - list of disks, $d$ - mapped coming disk, $p$ - point will be base point\\
        \textbf{Output:} $true|false$  is there a intersection\\ 
        \textbf{function} isIntersect$(l, d, p)$
    \end{flushleft}
    \begin{algorithmic}[1]
        \State $tmp_list \gets null$
        \State $max\_x\gets d.x+d.r$
        \State $min\_x\gets d.x-d.r$

>>>>

\section{Implementation}
Our code is available at ... (make a clean release!)
In practice, It's needed to transmit raw data which has multi-parameters
to clients e.g. Accelerometer, Euler Angle and Magnetometer etc.
Most of previous paper just force on single dimension sensor
data Compression. So we purpose a method to compress multi-dimensional
sensor data named LTC-D. It is used as linear estimation method.
Same as usual estimation compression method,  distance(different)
with compressed data from LTC-D and original data would not exceed
the predefined error range. We need to find line to represent
original data, it means the lines pass through datas' error range.
But in stream data, time seires data, it is difficult, because
all data do not show in same time plane. So this method will
mapping all data into one time plane. Then for each mapped error
range of data, check if there is intersection among them. If so means
there is a line could represent original data, and vice versa.

The method as below: assume the stream $i_{th}$ data
$D_i = (x_{i1}, x_{i2}, ..., x_{in},t_i)$, the first data $D_0$ would
be save as base point $Z=(z_{1}, z_{2}, ..., z_{n},t_z)$in the Method.
As usual, the timestamp after basepoint would be set as mapping plane.
We also need to record the intersect $S$ for find result lines.
The first data $D_1$ would change into tolerance range $R_1$.
initializing $S = R_1$. For each follow data$ D_i, i>1$, mapping $D_1$
into $\hat{D_1}$ = $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$,
and error margin after mapping should be $\frac{\epsilon}{t_i-t_z}$
on $\hat{x_{ij}}, j={1...n}$. The tolerance range after R_i, intersect
with S, if there is overlap, update S = S intersect R_i. If not, the base point
would be transmited and select a point in S as base point with timestamp $t_{i-1}$.

\todo{refector}
At beginning of the algorithm, we need a base point (which we will call \textit{z}) and bounding box which has upper and lower bound for each parameter respectively.Then start the algorithm.
\begin{enumerate}
  \item Initialization: Get first data point, and set point \textit{z} equals to first data point. Get the second data point $(x_{21},...,x_{2n},t_2)$, and assign each upper bound $U_j = x_{2j}+\frac{\epsilon}{t_2-t_1}$ and lower bound $L_j = x_{2j}-\frac{\epsilon}{t_2-t_1}$ where $j=\{1...n\}$.
  \item Get next data point, map the data point $(x_{i1},...,x_{in},t_i)$ into $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
  \item For each parameter(dimension) \textit{j}, if upper bound $U_j$ smaller than $x_{ij}-\frac{\epsilon}{t_i-t_1}$ or lower bound $L_j$ bigger than $x_{ij}+\frac{\epsilon}{t_i-t_1}$, then \textbf{goto 5}, else $U_j = min(U_j, x_{ij}+\frac{\epsilon}{t_i-t_1})$, and $L_j = max(L_j, x_{ij}-\frac{\epsilon}{t_i-t_1})$.
  \item Goto 2.
  \item output \textit{z} data point.
  \item Reset: set data point \textit{z} equals to center of the bounding box with time-stamp $t_{i-1}$, and $U_j=x_{ij}+\frac{\epsilon}{t_i-t_{i-1}}$, $L_j =x_{ij}-\frac{\epsilon}{t_i-t_{i-1}}$ with $j=\{1...n\}$.
  \item Goto 2.
  \item After all, output \textit{z} data point and center of bounding box respectively.
\end{enumerate}

for tolerance range, it depends on EPSILON and different type of distances for EPSILON.
If we using Manhattan distance to create tolerance range, it would become rectangle in 2D and cube for 3D.
But the tolerance range wold become disk or ball in 2D and 3D respectively, by using Euclidean distance.
\todo{maybe need a graphic}
\todo{below content is useful? }
\subsection{Multidimensional LTC with Manhattan distance}

In practice, Multidimensional LTC is same as implementing LTC in each 
parameter respectively. But we did some changes in our method. Assume 
$(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with 
n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., 
z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming 
data to $t_1$ time-stamp and create a bounding box for recording 
overlapping range which includes upper and lower bound for each 
dimension base on $t_1$. cause the time different between two adjacent 
data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + 
\frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$. 
After that updating tolerance range by adding designed error margin 
which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, 
j={1...n}$ with Manhattan distance. checking if there is overlap 
between tolerance and bounding box.The algorithm is as follows.

@@

\subsection{Multidimensional LTC with Euclidean distance}
In Euclidean distance version, we also map the coming data into same 
time-stamp $t_1$ the timestamp after base point. The difference with 
Manhattan distance version is that recording overlapping part with
a post-designed model is difficult, which need retain several arcs in 
2-dimension, or convex surfaces in 3-dimension. In our method, we will 
record all tolerance range for every mapped data which come from base 
data point until coming data point, in order to checking if there is 
intersection among them. For instance, in 3D-t, assume we have a the 
base point $Z = D_0$ and the tolerance range $R_1$ which is a ball 
as the intersection S. we need a list L to record mapped balls 
from $D_1$ to coming data. For each comming data $D_i, i>1$ mapping 
this data into $t_1$, and add it into list. Then the work is check out 
if all balls intersect, and form a public intersection. The method is 
based on plane sweep and binary search. At first, select one parameter, 
such as x-axis, finding a bounding range of all balls $B_i$ in x-axis. 
suppose $Max_bound_x = Min{1..n}{B_i.center.x + EPSILON/i}$, and 
$Min_bound_x = Max{1..n}{B_i.center.x - EPSILON/i}$. If there is overlap 
among balls, then the axis of the points inside intersection must located 
between Min_bound_x and Max_bound_x. Using binary search to select 
mid_x = (Min_bound_x + Max_bound_x)/2, then calculate a y-axis bounding 
with the plane x = mid_x. If the get bounding range in y-axis where 
$Max_bound_y > Min_bound_y$ and using binary search again to find mid_y, 
It means there is a line x=mid_x, Max_bound_y>= y >= Min_bound_y, 
parallels z-axis, could pass through all balls. Finally, in z-axis, 
computing bounding range, and If $Max_bound_z > Min_bound_z$, there 
must be one or more points inside all balls. The problem be solved. 
If the loop of binary search in x-axis overs, then there is no public 
intersection among balls, and need to transmit and update base point. 
In this method we need O(n*logn*logn) time complexity for binary search 
in x-axis and y-axis and traversal all balls in z-axis, also O(n) space 
complexity is needed for maintaining list. According this method, 
it could be extended into N-dimensional data. The main idea is to search, 
dimension by dimension, from a room or plane or line and get intersection 
point finally.

\todo{below content is useful? }
In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
\begin{itemize}
\item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk. After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data. Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
\item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis. So In 3-dimension whether \textit{n} balls intersect need to be check.
\end{itemize}

At first, let us solve the \textit{n} disks intersect. We use a algorithm which is based on plane sweep and dichotomy. Assume a disk include center$(x,y)$ and radius $r$. The pseudo-code in Algorithm 1.

\begin{algorithm}
    \caption{whether disks intersect}
    \begin{flushleft}
        \textbf{Input:} $l$ - list of disks, $d$ - mapped coming disk, $p$ - point will be base point\\
        \textbf{Output:} $true|false$  is there a intersection\\ 
        \textbf{function} isIntersect$(l, d, p)$
    \end{flushleft}
    \begin{algorithmic}[1]
        \State $tmp_list \gets null$
        \State $max\_x\gets d.x+d.r$
        \State $min\_x\gets d.x-d.r$
